PANCHANGE_data_preprocessing

### 2020-10-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
a few summaries had the wrong variable name

summary(dat$phq.diff_score_prepan_retro)

@@

summary(dat$phq.diff_score_prepan_base)
}

@@

summary(dat$gad.diff_score_prepan_base)
}

@@

summary(dat$pcl.diff_score_prepan_base)
}
```

@@

summary(dat$ocir.diff_score_prepan_base)
}
# Difference score for retrospective and baseline ocir sum scores
dat <- dat %>%
  mutate(
    ocir.diff_score_base_retro =
      as.numeric(
        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

>>>>

summary(dat$phq.diff_score_retro_prepan)

@@

summary(dat$phq.diff_score_base_prepan)
}

@@

summary(dat$gad.diff_score_base_prepan)
}

@@

summary(dat$pcl.diff_score_base_prepan)
}
```

@@

summary(dat$ocir.diff_score_base_prepan)
}
# Difference score for retrospective and baseline ocir sum scores
dat <- dat %>%
  mutate(
    ocir.diff_score_base_retro =
      as.numeric(
        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )
